\documentclass[11pt]{report}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}%english gestion
\usepackage[bottom]{footmisc}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage[newparttoc]{titlesec}
\usepackage[export]{adjustbox}
\usepackage[margin=0.95in]{geometry}
\usepackage{hyperref}

%All the packages
\usepackage{url,ragged2e,textcomp,color,nameref}
\usepackage{graphicx,xcolor,float,afterpage,paralist}
\usepackage{chngcntr,csquotes,mathptmx,lastpage,datatool}
\usepackage{subcaption,wrapfig,fancyhdr,blindtext}
\usepackage{titletoc,transparent,enumitem,listings}

%Nouvelles commandes
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\Mline}{\hrule \mbox{}\\[0.1cm]}
%\renewcommand{\thechapter}{\Roman{chapter}}

%final page
\newcommand\blankpage{%
\null
\thispagestyle{empty}%
\addtocounter{page}{-1}%
\newpage
}

%Afficher seulement part > chapitre > section dans la toc
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{1}

%Espacement des lignes
\renewcommand{\baselinestretch}{1.5} 

%Footer style
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}% Remove header rule
\fancyhead{}
\renewcommand{\footrulewidth}{0.4pt}% Add footer rule
\fancyfoot{}
\lfoot{Pierre THUBÉ \\ Azarias BOUTIN}
\rfoot{\thepage}

%Format de part
\newcommand{\partbreak}{\clearpage}
\titleclass{\part}{straight}
\titleformat{\part}[hang]
	{}
	{\Large \bfseries \thepart. \hspace{0.1cm} }
	{0pt}
	{\Large \bfseries }
\titlespacing*{\part}{0pt}{0pt}{18pt}

%FORMAT DU chapitre
\titleclass{\chapter}{straight}
\titleformat{\chapter}[hang]
  {}
  {\normalfont \bfseries \thechapter. \hspace{0.1cm} }
  {0pt}
  {\normalfont \bfseries }
\titlespacing*{\chapter}{0pt}{20pt}{15pt}

%FORMAT De section
\renewcommand*\thesection{\arabic{section}}
\titleclass{\section}{straight}
\titleformat{\section}[hang]
  {}
  {\normalfont \hspace{1cm} \bfseries \thesection . }
  {0pt}
  {\normalfont \bfseries }


%FORMAT De subsection
\titleclass{\subsection}{straight}
\titleformat{\subsection}[hang]
  {}
  {\small \hspace{2cm} \bfseries \thesubsection . }
  {0pt}
  {\small \bfseries }
  

%Comptage des figures
\renewcommand{\thefigure}{\arabic{figure}}

%Ne pas reset le numéro des figures  à chaque chapitre
\counterwithout{figure}{chapter}

%Reset numéro des chapitres dans chaque parties
\makeatletter
\@addtoreset{chapter}{part}
\makeatother  

%Coloration syntaxique du C++
\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\definecolor{darkgreen}{rgb}{0.0, 0.2, 0.13}

\lstset{
    backgroundcolor=\color{lbcolor},
	language=C++,
	captionpos=b,
	tabsize=3,
	frame=lines,
	numbers=left,
	numbersep=5pt,
	breaklines=true,
	showstringspaces=false,
	basicstyle=\footnotesize\ttfamily\bfseries\color{black},
	keywordstyle=\color[rgb]{0.1,0,1},
	commentstyle=\color[rgb]{0.300,0.300,0.300},
	stringstyle=\color[rgb]{0.627,0.126,0.100},
	numberstyle=\color[rgb]{0.73, 0.142, 0.900}
 }
 
 %List de mot ordonné
\newcommand{\sortitem}[1]{%
  \DTLnewrow{list}% Create a new entry
  \DTLnewdbentry{list}{description}{#1}% Add entry as description
}
\newenvironment{sortedlist}{%
  \DTLifdbexists{list}{\DTLcleardb{list}}{\DTLnewdb{list}}% Create new/discard old list
}{%
  \DTLsort{description}{list}% Sort list
  \begin{center}
	  \begin{inparaitem}%
    		\DTLforeach*{list}{\theDesc=description}{%
         \item \theDesc \hspace{0.1cm} }% Print each item
      \end{inparaitem}•%  
  \end{center}
}

\input{keywords.tex}
  
\begin{document}


\begin{titlepage}
\begin{center}


% Title
\Mline
{ \LARGE QTypingTest \\[0.4cm] }
\Mline
% Author and supervisor

Supervisor : Mark Cummins\\[3cm]

Thubé Pierre B00092354\\
Boutin Azarias B00092351\\[2cm]
BN013 BSC in Computing

\end{center}
\end{titlepage}

\setcounter{page}{2}

\tableofcontents
%'Page' dans la toc
\addtocontents{toc}{~\hfill\textbf{Page}\par }

%Partie Pierre
\input{pierre.tex}


%Partie Azarias
\input{azarias.tex}


%------------------------------------%
% Début Partie commnune				%
%------------------------------------%
\part{Personal reflections on project experiences}
Personal reflections on project experiences

\chapter{Pierre Thubé}
In view of the final software, I think we can say that principal goals has been reach. This project bring me knowledge in C++ and about the framework Qt. However, it also show me some of my weaknesses for example about how fast I am working. I would have like to be able to do more and so to learn more. However with all works we had during the year, the gap of level between Azarias and me about C++ and our way to learn new things, I had the feeling sometimes to be outworn by all the amount of work. However, I am still satisfied to have discovered Qt framework and this project confirm me that I prefer computer language like C++ or Java (object oriented language).\\
I also discovered how was working git and even if we was just using bases, it will be helpful for the next time I will need it. 

\chapter{Azarias Boutin}
I am quite satisfied with the software developed. When the group started the project, I was knowing nothing about Qt and wanted to learn as much as possible about this amazing framework. I knew the basics of C++ and felt this would be enough to build a good software. I also knew the basics of GUI thanks to the lessons with java swing. I really felt that this project bring me a lot of knowledge. During the implementation of the software, the several improvement steps proved this point.\\
However, I also feel like the project was not progressing fast enough. Maybe because of a lack of communication but also because of lack of knowledge from the other group member. Furthermore, since the group was only composed of two members, I felt like I was carried all the project from the beginning to the end.\\
Overall I am satisfied with the result and the software developed. It was a rich experience, and I learned a lot about Qt. I also learned a lot about git and version management system.


\input{appendix.tex}

\end{document}